---
title: "Initial medical data preparation"
author: "Tejasvini Mavuleti"
date: "2022-08-03"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prepare for initial analysis

```{r }
set.seed(123)
library(lubridate)
library(ggplot2)
library(randomForest)
library(dplyr)
library(rpart)
library(caret)
library(e1071)
library(corrplot)
```

## Functions to clean datasets

Read data sets from csv file
```{r }
clean_dataset <- function() {
  datasetloc = "C:/Users/mavul/OneDrive/Desktop/Health care data.csv"
  if (file.exists(datasetloc)) {
    data <- read.csv(file=datasetloc, header = T)
  }
  return(data)
}
```

Partition
#The data were partitioned into a test and training set using a 70/30 split
```{r }
set.seed(100)
train <- sample(nrow(clean_dataset()), 0.7*nrow(clean_dataset()), replace = FALSE)
TrainSet <- clean_dataset()[train,]
TestSet <- clean_dataset()[-train,]
summary(TrainSet)
summary(TestSet)
```

## Analysing the disease

The data set will predict the marital status with selected attributes that contributes to the analysis 
```{r}
disease_TrainSet <- select(TrainSet, gender, employment_status, education, marital_status, ancestry, disease)
disease_TestSet <- select(TestSet, gender, employment_status, education, marital_status, ancestry, disease)
disease_TrainSet$disease <- as.factor(disease_TrainSet$disease)
```


## Logistic Regression Model

The model was fit using a binomial logistic regression with the glm function in R, with family = binomial on the training data.
```{r}
fit <- glm(disease~.,data=disease_TrainSet,family=binomial())
summary(fit) 
confint(fit) 
exp(coef(fit)) 
exp(confint(fit)) 
#predict(fit, type="response") 
#residuals(fit, type="deviance") 
```


## Performance

Probabilities for the response variable based on the test data were assigned using the predict function.
```{r}
#probs <- predict(fit, test, type = "response")
#pred <- predict(fit, newdata = TestSet)
#pred
```

## Confusion Matrix
```{r}
#confusionMatrix(pred, TestSet$disease)
```


## Random forest model

Apply randomforest model
```{r}
# Fine tuning parameters of Random Forest model
model2 <- randomForest(disease ~ ., data = disease_TrainSet,  importance = TRUE)
model2

# Predicting on train set
predTrain <- predict(model2, disease_TrainSet, type = "class")

# Checking classification accuracy
table(predTrain, disease_TrainSet$disease) 
model2 <- na.omit(model2) 

# Predicting on Validation set
predValid <- predict(model2, disease_TestSet, type = "class")

# Checking classification accuracy
mean(predValid == disease_TestSet$disease)                    
table(predValid,disease_TestSet$disease)

# To check important variables
importance(model2)        
varImpPlot(model2) 
```

## Naive Bayes Model

```{r}
NBclassfier = naiveBayes(disease~., data=disease_TrainSet)
print(NBclassfier)
```

## Performance

Probabilities for the response variable based on the test data were assigned using the predict function.
```{r}
probs <- predict(fit, type = "response")
pred <- predict(fit, newdata = TestSet)
pred
```

## Confusion Matrix
```{r}
#confusionMatrix(pred, TestSet$disease)
```


## Random forest model

Apply random forest model
```{r}
# Fine tuning parameters of Random Forest model
model2 <- randomForest(disease ~ ., data = disease_TrainSet,  importance = TRUE)
model2

# Predicting on train set
predTrain <- predict(model2, disease_TrainSet, type = "class")

# Checking classification accuracy
table(predTrain, disease_TrainSet$disease) 
model2 <- na.omit(model2)

# Predicting on Validation set
predValid <- predict(model2, disease_TestSet, type = "class")

# Checking classification accuracy
mean(predValid == disease_TestSet$disease) 
table(predValid,disease_TestSet$disease)

# To check important variables
importance(model2)        
varImpPlot(model2) 
```

## Naive Bayes Model

```{r}
NBclassfier = naiveBayes(disease~., data=disease_TrainSet)
print(NBclassfier)
```